Storing messages with multipartite neural cliques

### 2014-07-11 Articles/article.tex
...

	\begin{figure}[!htb]
		\includegraphics[width=8.5cm]{Courbes/densiteexemple.pdf}
		\caption{Theoretical and empirical densities}
			\label{densiteth}
	\end{figure}

@@

	If $\gamma$ is big,
	$P(\mbox{no other vertex activated in this cluster})= \sum_{n = 1}^{a (c - c_e)} \left [ \sum_{k = 1}^{a} { a \choose k }   P(n_{v_c} = n)^k P(n_{v_c} > n)^{a-k} \right ] P(n_v < n)^{l-a}$%[ \sum_{x = 0}^{n - 1} P(n_v = x) \right]^{l-a }$

	\newpage

	%P(\mbox{no other vertex activated in any cluster})
	\begin{align*}
	P_{retrieve}=  \Bigg ( \sum_{n = 1}^{a ( c- c_e)} \left [ \sum_{k = 1}^{a} { a \choose k }   P(n_{v_c} = n)^k P(n_{v_c} > n)^{a-k} \right ]\\
	\left [ \sum_{x = 0}^{n - 1} P(n_v = x) \right]^{l-a } \Bigg)^{c_e}	
	\end{align*}
	\newpage
	%$\,$
	%\newpage
	\begin{figure}[!htb]
		\includegraphics[width=8.5cm]{Courbes/thpsi_c8l256e4}
		\caption{$\psi = 0.05$, 2 activities per cluster, 8 clusters, 256 units per cluster, 4 erasures, each point is the mean of 10 networks with 1000 sampled messages, analytical result in continuous black}
		\label{psith}
	\end{figure}

@@

	Absolute values of slopes diminish for increasing number of activities per cluster. We can conclude multipartite cliques improve the resilience of the network.

>>>>

	\begin{figure}[!htb]
		\includegraphics[width=8.5cm]{Courbes/remplacement_densite_c8l256a4}
		\caption{Theoretical and empirical densities}
			\label{densiteth}
	\end{figure}

@@

	The probability for all correct units to achieve a score equal or greater than $x$, with at least one achieving a score of $x$ is $P_c (x) =\sum_{k = 1}^{a} { a \choose k }   P(n_{v_c} = x)^k P(n_{v_c} > x)^{a-k} $

	If $\gamma$ is big enough,
	$P(\mbox{no other vertex activated in this cluster})= \sum_{x = 1}^{a (c - c_e)} P_c(x) P(n_v < x)^{l-a}$%[ \sum_{x = 0}^{n - 1} P(n_v = x) \right]^{l-a }$

	%P(\mbox{no other vertex activated in any cluster})
%	\begin{align*}
%	P_{retrieve}=  \Bigg ( \sum_{n = 1}^{a ( c- c_e)} \left [ \sum_{k = 1}^{a} { a \choose k }   P(n_{v_c} = n)^k P(n_{v_c} > n)^{a-k} \right ]\\
%	\left [ \sum_{x = 0}^{n - 1} P(n_v = x) \right]^{l-a } \Bigg)^{c_e}	
%	\end{align*}

	\begin{align}
	P_{retrieve}=  \left( \sum_{x = 1}^{a ( c- c_e)} P_c(x) P(n_v <x)^{l-a} \right )^{c_e}
	\label{psi_formula_th}
	\end{align}

	\begin{figure}[!htb]
		\includegraphics[width=8.5cm]{Courbes/thpsi_c8l256e4}
		\caption{$\psi = 0.05$, 2 activities per cluster, 8 clusters, 256 units per cluster, 4 erasures, each point is the mean of 10 networks with 1000 sampled messages, analytical result in continuous black}
		\label{psith}
	\end{figure}

@@

	Absolute values of slopes diminish for increasing number of activities per cluster. We can conclude usage of multipartite cliques improve the resilience of the network.
